Verifying Demonstrations

### 2017-09-21 intro.tex
Improves overview of the idea

There are three requirements for 
verification~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[V]
\item\label{EligibilityVerif} Eligibility: anyone can verify that each vote 
  cast is legitimate.
\item\label{UniversalVerif} Universal verifiability: anyone can verify that the 
  result is according to the cast votes.
\item\label{IndividualVerif} Individual verifiability: every voter can verify 
  that their vote is included in the result.
\end{requirements}
\end{frame}
We translate the votes into \emph{proofs of participation}.
Both universal and individual verifiability remain the same.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility --- that each proof of participation satisfies some temporal and 
spatial relation to the protest.
We will define these more formally in \cref{Verification}.

There are also three requirements for 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{frame}
\begin{requirements}[P]
\item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
  individual vote.
\item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
  provide any data that can be used as a proof of how the voter voted.
\item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
  with a coercer to prove the vote was cast in any particular way.
\end{requirements}
\pause{}
\mode<presentation>{%
  \begin{remark}
    P\ref{CoercionResistance} \(\implies\)
    P\ref{ReceiptFreeness} \(\implies\)
    P\ref{VotePrivacy}
  \end{remark}
}
\end{frame}
\Textcite{VerifyingPrivacyPropertiesOfVotingProtocols} showed that 
\cref{CoercionResistance} implies \cref{ReceiptFreeness}, which in turn implies
\cref{VotePrivacy}.
We note that we cannot improve the privacy of participating protesters, if they 
are caught during a protest there is nothing we can do.
But if they participate and they are not caught, then using our proposed tool 
should not incur any additional risk.
Thus we will adapt the idea of receipt freeness (see \cref{Privacy} for a 
detailed definition).
In essence, upon completing the protocol, Alice will have nothing that Eve can 
use to tie her to her participation proof.

>>>>

Voting has three requirements for 
verifiability~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}.
\begin{itemize}
  \item Eligibility: anyone can verify that each vote cast is legitimate.
  \item Universal verifiability: anyone can verify that the result is according 
    to the cast votes.
  \item Individual verifiability: every voter can verify that their vote is 
    included in the result.
\end{itemize}
We translate the votes into \emph{proofs of participation}.
Universal and individual verifiability remain the same: anyone can verify the 
participation count by counting the proofs.
The eligibility requirement is slightly different:
for protests the eligibility requirement must include temporal and spatial 
eligibility, i.e.\ that each proof of participation satisfies some temporal and 
spatial relation to the protest.
In essence, the proof must bind the person to the time and location of the 
protest.
We will define these more formally in \cref{Verification}.

There are also three levels of 
privacy~\cite{VerifyingPrivacyPropertiesOfVotingProtocols}:
\begin{itemize}
  \item\label{VotePrivacy} Vote privacy: the voting does not reveal any 
    individual vote.
  \item\label{ReceiptFreeness} Receipt freeness: the voting system does not 
    provide any data that can be used as a proof of how the voter voted.
  \item\label{CoercionResistance} Coercion resistance: a voter cannot cooperate 
    with a coercer to prove the vote was cast in any particular way.
\end{itemize}
We note that we cannot improve the privacy of participating protesters, if they 
are caught during a protest there is nothing we can do.
But if they are not caught in the act, then using our proposed tool should not 
incur any additional risk.
Thus we will adapt the idea of receipt freeness (see \cref{Privacy} for a 
detailed definition) to the protest context.
In essence, upon completing the protocol, Eve cannot link Alice to Alice's 
participation proof --- even with Alice's cooperation.
